Selecting Team Members of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics Based on Performance and Stability To Maximize Success

### 2024-01-15 manuscript/submission.tex
cleaned bib and fixed compiling errors
changing title for appropriateness

\title{Predicting The Success of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics 
Using Mean and Standard Deviation Derived Parameters}
\author{Kathleen Houlihan\\
  Department of Statistics\\
  University of Connecticut
}

@@

@@

\\

>>>>

\title{Selecting Team Members of The Female United States Artistic Gymnastics Team at The 2024 Paris Olympics 
Based on Performance and Stability To Maximize Success}
\author{Kathleen Houlihan\\
  Department of Statistics\\
  University of Connecticut
}

@@

\citet{JonasRohleder2023} did something...

@@
